---
title: "Predicting AI Job Automation Risk - Report"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
source("R/utils.R")
```

# Summary

This report shows pipeline results for AI automation risk analysis across software engineering roles.

# Data

```{r}
occ <- readr::read_csv("data/processed/occupations_features.csv", show_col_types = FALSE)
head(occ)
```

# Top Risky Roles

```{r}
occ %>% arrange(desc(risk_score)) %>% head(10) %>% knitr::kable()
```

# Visualizations

```{r, fig.width=10, fig.height=6}
occ %>%
  ggplot(aes(x = reorder(job, risk_score), y = risk_score)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(title = "AI Automation Risk by Role", x = "", y = "Risk Score") +
  theme_minimal()
```

# Model Performance

```{r}
if(file.exists("output/model_metrics.csv")) {
  metrics <- readr::read_csv("output/model_metrics.csv", show_col_types = FALSE)
  knitr::kable(metrics)
} else {
  cat("Model metrics not available. Run 04_modeling.R first.")
}
```

# Conclusion

- AI automation risk varies significantly across software roles
- Roles with higher routine task shares and higher AI capability scores face greater risk
- Skills development and upskilling are recommended to mitigate automation exposure
